\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-30 paper/main.tex
minor updates

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two 
types of features: structural information for drugs and proteins that
can be used to determine if they may physically interact, and
information about drug effects that may localize on an interaction
network.

@@

For a given protein, we want to find all suitable interacting drugs, \textbf{among a set of known drugs}.
To obtain a prediction for a given drug-protein pair, we first
build representations embodying both phenotypes and functions for both drugs and proteins, while also preparing structural, molecular representations, e.g., utilizing DL2vec over PhenomeNET and the prebuilt features from SMILES transformer and DeepGOPlus. Note that this approach can be easily generalized, profiting from other protein function and phenotype representation methods. \\ 
Hence, we pretrain the siamese networks for both molecular and ontology features, yielding the deep neural network transformers (DNNT) for both methods, and both drugs and proteins, individually. These embeddings are now added to the graph neural network as node features, where we start an end-to-end learning and training process. Notably, like in the pretraining phase, we rely on siamese neural networks, enforcing similar representations for fitting drug-protein pairs. The overall architecture is depicted in Figure~\ref{fig:Fullmodel}.\\

>>>>

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank known drugs that likely target this protein. \name combines two 
types of features: structural information for drugs and proteins that
can be used to determine if they may physically interact, and
information about drug effects that may localize on an interaction
network.
As structural features, \name uses structural representations of drugs
from the SMILES transformer \cite{} and representations of protein
amino acid sequences from DeepGOPlus \cite{}.
\name learns representations of drug effects and protein functions
using the ontology-based machine learning method DL2Vec \cite{}.

We use two Siamese neural networks to combine the molecular
and phenotype representations of drugs and proteins,
% and
% ontology features, yielding the deep neural network transformers
% (DNNT) for both methods, and both drugs and proteins,
% individually. 
and add these to a protein interaction network as node features.
% neural network in which nodes representing interactions
% between proteins as node features, 
We then train this model in an end-to-end manner. % Notably, like in the
% pretraining phase, we rely on siamese neural networks, enforcing
% similar representations for fitting drug-protein pairs. 
The overall architecture is depicted in Figure~\ref{fig:Fullmodel}.

% For a given protein, we want to find all suitable interacting drugs, \textbf{among a set of known drugs}.
%To obtain a prediction for a given drug-protein pair,

Note that this approach can be easily generalized, profiting from
other protein function and phenotype representation methods.

@@
